[dcpo_demsupport]

### 2020-06-06 paper/dcpo_demsupport.Rmd
add data/claassen_input.csv

>>>>

```{r replication-data-prep, eval=FALSE}
claassen_input_raw <- DCPOtools:::claassen_setup(vars = read_csv("data-raw/mood_dem.csv"),
                                       file = "data/claassen_input_raw.csv")

claassen_input <- format_claassen(claassen_input_raw)

claassen_m5 <- stan(file = 'R/supdem.stan.mod5.stan',
                       data = claassen_input,
                    iter = 2000,
                    chains= 4,
                    cores = 4,
                    thin = 2,
                    pars = c("mu_lambda", "sigma_lambda", "sigma_delta", "sigma_theta", "phi", "lambda", "delta", "theta", "x_pred","log_lik"),
                    control = list(adapt_delta=0.99, stepsize=0.02, max_treedepth=11))

```
